---
title: "Dataset Picker"
author: "Heiko Lange"
date: "1 Februar 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Problem/Opportunity
<hr>

* You have an idea you want to try in R, but you are missing the right dataset?
* You remember there was this interesting timeseries, but you forgot the name of it?
* You found a new package but have no idea what datasets it provides?

<br>
<hr>
<h1>Look no further!</h1>

## Value Proposition
<div class="columns-2">

* DatasetPicker saves you countless hours of time searching for the right dataset
* Filter by data type, # Observations, # Variables or search by name
* Look into almost any package you like and have installed on the server

```{r out.width="400px", out.height="300px"}
library(ggplot2)

df <- data.frame(UsageDatasetPicker = c("Without", "With"), values = c(10, 1))
g <- ggplot(df, aes(UsageDatasetPicker, values)) +
    geom_bar(stat = "identity", aes(fill = UsageDatasetPicker)) +
    labs(x = "") + labs(y = "Approx. search time in minutes") +
    ggtitle("Time spend searching the right dataset") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.direction = "horizontal", legend.position = "bottom")
g
```
<span style="font-size: 12px;">(Survey not representative - there was only participant)</span>
</div>

## Underlying Magic
<hr>

* DatasetPicker will scan through a given package and analyses it datasets
* DatasetPicker gives you filter options based on the datasets of that package
* DatasetPicker can browse through all your installed packages
* DatasetPicker standardized different formats

<br>
<hr>
<h1>Did you know, that ggplot2 brings its own data?</h1>

## DatasetPicker - look for yourself

<hr>
<br>

* Find the slides on [Rpubs](http://rpubs.com/Loradim/datasetpicker/)

* Or go directly to the [DatasetPicker App](https://loradim.shinyapps.io/datasetpicker/)

* Sourcecode can be found in my [github repository](https://github.com/Loradim/DatasetPicker)
